\documentclass[5p]{elsarticle}			% 5p gir 2 kolonner pr side. 1p gir 1 kolonne pr side.
\journal {Veileder}
\usepackage[T1]{fontenc} 				% Vise norske tegn.
%\usepackage[norsk]{babel}				% Tilpasning til norsk.
\usepackage{graphicx}       				% For å inkludere figurer.
\usepackage{amsmath,amssymb} 			% Ekstra matematikkfunksjoner.
%\usepackage{siunitx}					% Må inkluderes for blant annet å få tilgang til kommandoen \SI (korrekte måltall med enheter)
%	\sisetup{exponent-product = \cdot}      	% Prikk som multiplikasjonstegn (i steden for kryss).
% 	\sisetup{output-decimal-marker  =  {,}} 	% Komma som desimalskilletegn (i steden for punktum).
% 	\sisetup{separate-uncertainty = true}   	% Pluss-minus-form på usikkerhet (i steden for parentes). 
\usepackage{booktabs}                     		% For å få tilgang til finere linjer (til bruk i tabeller og slikt).
\usepackage[font=small,labelfont=bf]{caption}	% For justering av figurtekst og tabelltekst.
\usepackage{todonotes}


\makeatletter
\def\ps@pprintTitle{%
  \let\@oddhead\@empty
  \let\@evenhead\@empty
  \let\@oddfoot\@empty
  \let\@evenfoot\@oddfoot
}
\makeatother

\usepackage[utf8]{inputenc}		% gjør slik at vi kan skrive æ,ø,å mm.
\usepackage{parskip}
\usepackage{hyperref}
\usepackage[noabbrev,capitalize]{cleveref}
\usepackage{subcaption}
\usepackage{physics}

% Denne setter navnet på abstract til Sammendrag
\renewenvironment{abstract}{\global\setbox\absbox=\vbox\bgroup
\hsize=\textwidth\def\baselinestretch{1}%
\noindent\unskip\textbf{Abstract}
\par\medskip\noindent\unskip\ignorespaces}
{\egroup}


% Disse kommandoene kan gjøre det enklere for LaTeX å plassere figurer og tabeller der du ønsker.
\setcounter{totalnumber}{5}
\renewcommand{\textfraction}{0.05}
\renewcommand{\topfraction}{0.95}
\renewcommand{\bottomfraction}{0.95}
\renewcommand{\floatpagefraction}{0.35}
\newcommand{\e}{\mathrm{e}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{frontmatter}
\title{TFY4235 - The World of Quantum Mechanics}

\author[fysikk]{Karl Kristian Ladegård Lockert}
\address[fysikk]{Institutt for fysikk, Norges Teknisk-Naturvitenskapelige Universitet, N-7491 Trondheim, Norway.}
\begin{abstract}
When implementing different methods for solving the Schrödinger equation, we investigate the results and possible errors for three different systems, starting with a particle in a box. The computed energy eigenvalues are in good agreement with the analytic results for lower energies.  Introducing a potential barrier to the box, a tunneling phenomena occurs when preparing an initial 
state out of (almost) degenerate states and propagating over a suitable time span. 
Propagating the same initial state with the Crank-Nicolson scheme gives zero tunneling in the same time interval as in the plane-wave basis. The Euler-scheme is found unfit, attributed to the requirement of $H$ being unitary, which is not fulfilled. A relationship between the number of steps we are able to calculate (in the Euler scheme) and the discretization size, both spatial and temporal, is established. Lastly, a two-level system is studied. A numerical implementation of the time-evolution is presented,and used to compute the transition probabilities between two states. This is a result in good agreement with analytic approximations, with the added decoherence lowering the probability amplitude over time. 

\end{abstract}
\end{frontmatter}

\input{tex/introduction}
\input{tex/hamiltonian}
\input{tex/barrier}
\input{tex/roots}
\input{tex/step_by_step}

\bibliographystyle{unsrt}
\bibliography{bib}

\end{document}
